Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-22 paper.tex
remv paranthesis
ld hc assoc proof
minor fix
type in L
a little progress

	Reduction \fbox{$\judgeCreduce{s}{s}$}
	\[
	\begin{array}{rclr}
		\hiredrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{
			\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
%			\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa
		}
	}{}
	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\vOOfun{\rho}{x}{e})}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{\kOOconsI{e_2}{\rho}{\kappa}}
	}{}
	\redrule{
		\sOOinspect{\eOOinl{e}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\kOOinl{\kappa}}
	}{}
	\redrule{
	\sOOinspect{\eOOinr{e}}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{\kOOinr{\kappa}}
	}{}
	\redrule{
		\sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{\kOOappI{e_2}{\rho}{\kappa}}}{}

@@

\redrule{
\sOOreturn{v_2}{\kOOappII{\vOOfun{\rho}{x}{e}}{\kappa}}}{
\sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
	\hiredrule{
		\sOOreturn{v_1}{
			\kOOappII{\vOOcast{v_2}{
					\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			}}{\kappa}
%			(\mathtt{app_2} \; \vOOcast{v_2}{
%				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
%			} \; \kappa)
		}
	}{
		\sOOreturn{v_1}{
			\kOOcast{\cOOcast{T_3}{l}{T_1}}{
				\kOOappII{v_2}{
					\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}
				}
			}
%			\langle\rangle
%			(\mathtt{app_2} \; v_2 \; 
%			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa}
		}
	}{}
	\redrule{
	\sOOreturn{
		\vOOcons{v_1}{v_2}
	}{\kOOcar{\kappa}}
	}{
	\sOOreturn{v_1}{\kappa}
	}{}
	\hiredrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{\mathtt{fst} \; \kappa}
	}{
		\sOOreturn{v}{
			\kOOcar{
				\kOOcast{\cOOcast{T_1}{l}{T_3}}{\kappa}
			}}
	}{}
	\redrule{
	\sOOreturn{
	\vOOcons{v_1}{v_2}
	}{\kOOcdr{\kappa}}
	}{
	\sOOreturn{v_2}{\kappa}
	}{}

@@

\begin{figure}
	\[
	\begin{array}{rclr}
	\stxrule{I}{injectable types (\lazyD)}{
		\POOfun{T}{T} \mid \POOunit}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOfun{\TOOdyn}{\TOOdyn} \mid \POOunit
	}
	\stxrule{c}{coercions}{
		\ncInj{I} \mid
		\ncProj{I}{l} \mid
		\ncId \mid
		\ncFail{l} \mid
		\ncSeq{c}{c} \mid
		\ncFun{c}{c}
	}
	\stxrule{\bar{c}}{wrapper coercions}{	
		\ncInj{I} \mid
		\ncFun{\hat{c}}{\hat{c}} \mid
		\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
	}
%	\stxrulecont{
%		\ncProd{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncProd{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
%		\ncSum{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncSum{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid	
%	}
	\stxrule{\hat{c}}{normal coercions}{
		\bar{c} \mid
		\ncId \mid
		\ncFail{l} \mid
		\ncProj{I}{l} \mid
		\ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
		\ncSeq{\ncProj{I}{l}}{\ncInj{I}}
	}
	\stxrulecont{
		\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
		\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
	}
	\end{array}
	\]
	\caption{Syntax of coercions and normal forms}
	\label{fig:normal-coercion}
\end{figure}

\figref{fig:normal-coercion} gives the grammar for coercions, written
$c$ and also coercions in normal form, written $\hat{c}$.
%
To review, an injection $I!$ takes a value from an injectiable type
$I$ to type $\TOOdyn$. An injectable type is simply a type that can be
cast directly to (injection) and from (projection) $\TOOdyn$. The
definition of injectable type depends on blame strategy. With \lazyD,
all pre-types are injectable. With \lazyUD, only
$\POOfun{\TOOdyn}{\TOOdyn}$ is injectable.
%
A projection $I?^l$ takes a value from type $\TOOdyn$ to type $I$, or
halts the program and blames $l$ if the value is of a different type.
The coercion $\iota$ is the identity, $\bot^{l}$ is the coercion that
always fails and blames $l$, and $\ncSeq{c_1}{c_2}$ applies $c_1$ and
then $c_2$ in sequence. The function coercion $\ncFun{c_1}{c_2}$
applies $c_1$ to the argument of a function and $c_2$ to the return
value.

Coercions come with a reduction relation so it is natural to ask what
are their normal forms. The most important of the reduction rules are
the ones that handle when an injection is followed by a projection,
which for \lazyUD{} are:
\begin{align*}
  I! ; I?^l &\longmapsto \iota \\
  I_1! ; I_2?^l & \longmapsto \bot^l & \text{if } I_1 \neq I_2
\end{align*}
and the rule for pushing sequences below function coercions:
\begin{align*}
  (c_1 \to c_2) ; (c_3 \to c_4) & \longmapsto
  (c_3 ; c_1) \to (c_2 ; c_4)
\end{align*}
Of course there are also rules that remove identity coercions.

\todo[inline]{UNDER CONSTRUCTION -Jeremy}

Let $\bar{c}$ range over wrapper coercions, which represent casts in $
\vOOcast{v}{c}$.  Let $\hat{c}$ range over normal coercions. If we
inline $\bar{c}$ and re-order the cases, the definition of $\hat{c}$
becomes:
\[
\begin{array}{rclr}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} \mid
}
\end{array}
\]

Three observations on this definition leads to hypercoercion: 
\begin{enumerate}
	\item The length of normal coercion is at most three.
	\item Projections are always at the beginning when present.
	\item Injections and failures are always at the end when present.
\end{enumerate}

@@

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by
observations on coercion normal forms: a normal coercion has at most
three parts; projections are always at the beginning; injections and
failures are always at the end. Hypercoercions have similar shape: a
hypercion either is $\hyperCoercionI$, the identity cast for
$\TOOdyn$, or contains three parts, where the first part is either a
projection or a no-op while last part is either an injection, a
failure, or a no-op.

@@

\begin{proposition}[\lazyD\ hypercoercion is a monoid]
	\label{thm:hc-monoid}
	For all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{proposition}
\begin{proof}
	By induction on hypercoercion(s).
\end{proof}

@@

	Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
	\[
	\begin{array}{rclr}
	\hiredruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\hcvOOtt}{\kappa}
	}{}
	\hiredruleS{
		\sOOinspect{(\eOOlam{T_1}{T_2}{x}{e})}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{
			wrap(\kOOconsI{e_2}{\rho}{\kappa})
		}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{wrap(\kOOinl{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{wrap(\kOOinr{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{wrap(\kOOappI{e_2}{\rho}{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcar{e})}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{wrap(\kOOcar{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcdr{e})}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{wrap(\kOOcdr{\kappa})}}{}

	\redruleS{
		\sOOinspect{(\eOOcase{e_1}{e_2}{e_3})}{\rho}{\kappa}}{
		\sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
	\hiredruleS{
		\sOOreturn{v}{\kOOcast{c}{k}}
	}{
	\begin{cases}
	\continue{k}{v'} & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
	\\
	\sOOhalt{(\oOOblame{l})} & \sidecond{applyCast(v,c) = \rOOfail{l}}
	\end{cases}
	}{}
	\end{array}
	\]

@@

\hifunrule{
	\continue{v_2}{\kOOconsII{v_1}{\kappa}}}{
	\sOOreturn{(\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)})}{\kappa}}{}

\hifunrule{
	\continue{v}{\kOOinl{\kappa}}}{
	\sOOreturn{(\hcvOOinl{v}{id(T)})}{\kappa}}{}

\hifunrule{
	\continue{v}{\kOOinr{\kappa}}}{
	\sOOreturn{(\hcvOOinr{v}{id(T)})}{\kappa}}{}

@@

\hifunrule{
	\continue{v_2}{(\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa})}}{
\begin{cases}
\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
\sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
\\
\sOOhalt{l} \\
\sidecond{applyCast(v_2,c_1) = \rOOfail{l}}
\end{cases}
}{}

@@

\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
  \[
  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
  \]
\end{proposition}
\begin{proof}
	Without lost of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
	$\judgeSreduce{C_2}{e}{o}$.\\
	By the definition of $eval_{\mathcal{S}(C)}$, we know 
	\[
	\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_1)}(e)}{\sOOhalt{o}}
	\]
	By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
	have 
	\[\judgeSreduceTrans{C_2}{load_{\mathcal{S}(C_2)}(e)}{\sOOhalt{o}}\]
	that is, $\judgeSreduce{C_2}{e}{o}$
\todo[inline]{Induction on what? -JS
\\---\\
Fixed. -KC
\\---\\
Need to define load. -KC}
\end{proof}

>>>>

	Reduction \fbox{$\judgeCreduce{s}{s}$}
	\[
	\begin{array}{rclr}
		\hiredrule{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{
			\kOOcast{\cOOcast{T_1}{l}{T_2}}{\kappa}
%			\langle\cOOcast{T_1}{l}{T_2}\rangle\kappa
		}
	}{}
	\redrule{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOtt}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{\vOOfun{\rho}{x}{e}}{\kappa}
	}{}
	\redrule{
		\sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{\kOOconsI{e_2}{\rho}{\kappa}}
	}{}
	\redrule{
		\sOOinspect{\eOOinl{e}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{\kOOinl{\kappa}}
	}{}
	\redrule{
	\sOOinspect{\eOOinr{e}}{\rho}{\kappa}
	}{
	\sOOinspect{e}{\rho}{\kOOinr{\kappa}}
	}{}
	\redrule{
		\sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
	}{
\sOOinspect{e_1}{\rho}{\kOOappI{e_2}{\rho}{\kappa}}}{}

@@

\redrule{
\sOOreturn{v_2}{\kOOappII{(\vOOfun{\rho}{x}{e})}{\kappa}}}{
\sOOinspect{e}{\rho[x:=v_2]}{\kappa}}{}
	\hiredrule{
		\sOOreturn{v_1}{
			\kOOappII{\vOOcast{v_2}{
					\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
			}}{\kappa}
%			(\mathtt{app_2} \; \vOOcast{v_2}{
%				\cOOcast{\POOfun{T_1}{T_2}}{l}{\POOfun{T_3}{T_4}}
%			} \; \kappa)
		}
	}{
		\sOOreturn{v_1}{
			\kOOcast{\cOOcast{T_3}{l}{T_1}}{
				\kOOappII{v_2}{
					\kOOcast{\cOOcast{T_2}{l}{T_4}}{\kappa}
				}
			}
%			\langle\rangle
%			(\mathtt{app_2} \; v_2 \; 
%			\langle\cOOcast{T_2}{l}{T_4}\rangle \kappa}
		}
	}{}
	\redrule{
	\sOOreturn{
		\vOOcons{v_1}{v_2}
	}{\kOOcar{\kappa}}
	}{
	\sOOreturn{v_1}{\kappa}
	}{}
	\hiredrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{\mathtt{fst} \; \kappa}
	}{
		\sOOreturn{v}{
			\kOOcar{
				\kOOcast{\cOOcast{T_1}{l}{T_3}}{\kappa}
			}}
	}{}
	\redrule{
	\sOOreturn{
	\vOOcons{v_1}{v_2}
	}{\kOOcdr{\kappa}}
	}{
	\sOOreturn{v_2}{\kappa}
	}{}

@@

\begin{figure}
	\[
	\begin{array}{rclr}
	\stxrule{I}{injectable types (\lazyD)}{
		\POOfun{T}{T} \mid \POOunit}
	\stxrule{I}{injectable types (\lazyUD)}{
		\POOfun{\TOOdyn}{\TOOdyn} \mid \POOunit
	}
	\stxrule{c}{coercions}{
		\ncInj{I} \mid
		\ncProj{I}{l} \mid
		\ncId \mid
		\ncFail{l} \mid
		\ncSeq{c}{c} \mid
		\ncFun{c}{c}
	}
	%% \stxrule{\bar{c}}{wrapper coercions}{	
	%% 	\ncInj{I} \mid
	%% 	\ncFun{\hat{c}}{\hat{c}} \mid
	%% 	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}
	%% }
%	\stxrulecont{
%		\ncProd{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncProd{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
%		\ncSum{\hat{c}}{\hat{c}} \mid
%		\ncSeq{\ncSum{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid	
%	}
\stxrule{\hat{c}}{normal coercions}{
	\ncFun{\hat{c}}{\hat{c}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}} \mid
	\ncSeq{\ncProj{I}{l}}{\ncFail{l}}
}
\stxrulecont{
	\ncId \mid
	\ncProj{I}{l} \mid
	\ncInj{I} \mid
	\ncSeq{\ncProj{I}{l}}{\ncInj{I}} \mid
	\ncFail{l} 
}
	%% \stxrule{\hat{c}}{normal coercions}{
	%% 	\bar{c} \mid
	%% 	\ncId \mid
	%% 	\ncFail{l} \mid
	%% 	\ncProj{I}{l} \mid
	%% 	\ncSeq{\ncProj{I}{l}}{\ncFail{l}} \mid
	%% 	\ncSeq{\ncProj{I}{l}}{\ncInj{I}}
	%% }
	%% \stxrulecont{
	%% 	\ncSeq{\ncProj{I}{l}}{\ncFun{\hat{c}}{\hat{c}}} \mid
	%% 	\ncSeq{\ncProj{I}{l}}{\ncSeq{\ncFun{\hat{c}}{\hat{c}}}{\ncInj{I}}}
	%% }
	\end{array}
	\]
	\caption{Syntax of coercions and normal forms}
	\label{fig:normal-coercion}
\end{figure}

\figref{fig:normal-coercion} reviews the grammar for coercions,
written $c$.
%
To review, an injection $I!$ takes a value from an injectiable type
$I$ to type $\TOOdyn$. An injectable type is simply a type that can be
cast directly to (injection) and from (projection) $\TOOdyn$. The
definition of injectable type depends on blame strategy. With \lazyD,
all pre-types are injectable. With \lazyUD, only
$\POOfun{\TOOdyn}{\TOOdyn}$ is injectable.
%
A projection $I?^l$ takes a value from type $\TOOdyn$ to type $I$, or
halts the program and blames $l$ if the value is of a different type.
The coercion $\iota$ is the identity, $\bot^{l}$ is the coercion that
always fails and blames $l$, and $\ncSeq{c_1}{c_2}$ applies $c_1$ and
then $c_2$ in sequence. The function coercion $\ncFun{c_1}{c_2}$
applies $c_1$ to the argument of a function and $c_2$ to the return
pvalue.

Coercions come with a reduction relation so it is natural to ask what
are their normal forms. \figref{fig:normal-coercion} defines the
syntax of coercion in normal form, written $\hat{c}$. Conceptually, a
coercion in normal form has three parts, all of which are optional.
It may start with a projection $I?^l$, then it may be followed by a
function coercion, and then it may be concluded with an injection $I!$
or a failure $\bot^l$. While this is a simple idea, there are 10
clauses in the definition for $\hat{c}$!

%% Let $\bar{c}$ range over wrapper coercions, which represent casts in $
%% \vOOcast{v}{c}$.  Let $\hat{c}$ range over normal coercions. If we
%% inline $\bar{c}$ and re-order the cases, the definition of $\hat{c}$
%% becomes:
%% \[
%% \begin{array}{rclr}
%% \end{array}
%% \]

%% Three observations on this definition leads to hypercoercion: 
%% \begin{enumerate}
%% 	\item The length of normal coercion is at most three.
%% 	\item Projections are always at the beginning when present.
%% 	\item Injections and failures are always at the end when present.
%% \end{enumerate}

@@

This section presents our first contribution, the definition of
hypercoercions.  The design of hypercoercions is motivated by the
observation that a normal coercion has at most three parts;
projections are always at the beginning; injections and failures are
always at the end. Hypercoercions make this structure explicit: a
hypercion either is $\hyperCoercionI$, the identity cast for
$\TOOdyn$, or contains three parts, where the first part is either a
projection or the identity and the last part is either an injection, a
failure, or the identity.

\todo[inline]{What about the middlepart? -JS}

@@

\begin{proposition}[\lazyD\ hypercoercion is a monoid]
	\label{thm:hc-monoid}
	For all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{proposition}
\begin{proof} Part (1) and (2) are by induction on $c$. Part (3) is by 
induction on $c_2$ and case analysis on $c_1$ and $c_3$.
\end{proof}

@@

	Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
	\[
	\begin{array}{rclr}
	\hiredruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\hcvOOtt}{\kappa}
	}{}
	\hiredruleS{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)}}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOcons{e_1}{e_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{
			wrap(\kOOconsI{e_2}{\rho}{\kappa})
		}
	}{}
	\redruleS{
		\sOOinspect{\eOOinl{e}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{wrap(\kOOinl{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{\eOOinr{e}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{wrap(\kOOinr{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{\eOOapp{e_1}{e_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{wrap(\kOOappI{e_2}{\rho}{\kappa})}}{}

	\redruleS{
		\sOOinspect{\eOOcar{e})}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{wrap(\kOOcar{\kappa})}}{}

	\redruleS{
		\sOOinspect{\eOOcdr{e}}{\rho}{\kappa}}{
		\sOOinspect{e}{\rho}{wrap(\kOOcdr{\kappa})}}{}

	\redruleS{
		\sOOinspect{\eOOcase{e_1}{e_2}{e_3}}{\rho}{\kappa}}{
		\sOOinspect{e_1}{\rho}{wrap(\kOOcaseI{e_2}{e_3}{\rho}{\kappa})}}{}
	\hiredruleS{
		\sOOreturn{v}{\kOOcast{c}{k}}
	}{
	\begin{cases}
	\continue{k}{v'} & \sidecond{applyCast(v,c) = \rOOsucc{v'}} 
	\\
	\sOOhalt{\oOOblame{l}} & \sidecond{applyCast(v,c) = \rOOfail{l}}
	\end{cases}
	}{}
	\end{array}
	\]

@@

\hifunrule{
	\continue{v_2}{\kOOconsII{v_1}{\kappa}}}{
	\sOOreturn{\hcvOOcons{v_1}{id(T_1)}{v_2}{id(T_2)}}{\kappa}}{}

\hifunrule{
	\continue{v}{\kOOinl{\kappa}}}{
	\sOOreturn{\hcvOOinl{v}{id(T)}}{\kappa}}{}

\hifunrule{
	\continue{v}{\kOOinr{\kappa}}}{
	\sOOreturn{\hcvOOinr{v}{id(T)}}{\kappa}}{}

@@

\hifunrule{
	\continue{v_2}{\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa}}}{
\begin{cases}
\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
\sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
\\
\sOOhalt{l} \\
\sidecond{applyCast(v_2,c_1) = \rOOfail{l}}
\end{cases}
}{}

@@

\begin{proposition}[Equivalence of two \lazyD{} Cast ADTs]
  \label{thm:surely-lazyD-eqv}
  Assume $C_1$ and $C_2$ implements Lazy D Cast ADT,
  \[
  eval_{\mathcal{S}(C_1)} = eval_{\mathcal{S}(C_2)}.
  \]
\end{proposition}
\begin{proof}
	Without lost of generality, assume $\judgeSreduce{C_1}{e}{o}$, prove 
	$\judgeSreduce{C_2}{e}{o}$.\\
	By the definition of $eval_{\mathcal{S}(C)}$, we know 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
	By induction on this reduction sequence and Lemma~\ref{thm:CEKS-bisim}, we 
	have 
\[
\judgeSreduceTrans{C_2}{\sOOinspect{e}{\emptyset}{wrap(\kOOmt)}}{\sOOhalt{o}}
\]
	that is, $\judgeSreduce{C_2}{e}{o}$
\todo[inline]{Induction on what? -JS
\\---\\
Fixed. -KC}
\end{proof}
